---
title: "Ad_click_through_rate"
author: "Elamaran Jayabarathy"
date: "3/29/2022"
output: html_document
---


```{r setup}

knitr::opts_knit$set(root.dir = 'D:/Projects/Ad_click')
```


##library

```{r}
library(lubridate)
library(dplyr)
library(forecast)
library(caret)
library(rpart)
library(rpart.plot)

```
#load the datset

```{r}
ad.df<- read.csv("D:/TBANLT 560/Final_Exam/advertising.csv")

```
## Data pre-processing


```{r}

ad.df <- ad.df %>% mutate(Timestamp = mdy_hm(`Timestamp`))
ad.df<-ad.df %>%
  dplyr::mutate(month = lubridate::month(Timestamp), 
                day = lubridate::day(Timestamp),
                dayofweek= lubridate::wday(Timestamp, week_start = 1))


```



## Check for Imbalance of dependant data-- We have equal number yes/no

```{r}

barplot(prop.table(table(ad.df$Clicked.on.Ad)),
        col = rainbow(2),
        main = "Class Distribution")

```



## Exploratory Data  Analysis

## Summary Statistics
```{r}

summary(ad.df)
```


##What age group does the dataset majorly consist of?

```{r}

ggplot(data=ad.df,aes(x=Age))+
  geom_histogram(aes(x =Age),
                 bins=20,
                 color="black", 
                 fill="dodgerblue") +
  labs(title="Histogram for Age group",
         x= "Age")+
  geom_density(col=3)


```


### Income distribution for different age groups , clicked on Ad

```{r}
ad.df$Clicked.on.Ad <- as.factor(ad.df$Clicked.on.Ad)
ggplot(ad.df, aes(x = Age, y =Area.Income, colour = Clicked.on.Ad))+ 
  geom_point(size=2.5)


```

### Which age group is spending maximum time on the internet? and who clicked on Ad?

```{r}
ggplot(ad.df, aes(x = Age, y =Daily.Internet.Usage, colour = Clicked.on.Ad))+ 
  geom_point(size=2) +  scale_color_brewer(palette = "Set1")
##scale_color_grey(start = 0.8, end = 0.2)
#scale_color_manual(values = c("A" = "green", "B" = "red"))

```


### Ad click based on gender

```{r}
ggplot(ad.df, 
       aes(x = Male, 
           fill = Clicked.on.Ad)) + 
  geom_bar(position = "dodge")

```



### Visualizing Ad clicked on different time stamps


```{r}

cdplot(as.factor(Clicked.on.Ad) ~ month , data=ad.df)
cdplot(as.factor(Clicked.on.Ad) ~ day , data=ad.df)
cdplot(as.factor(Clicked.on.Ad) ~ dayofweek , data=ad.df)

```

## Check for correlation

```{r}
library(corrplot)

M<-cor(ad.df[, unlist(lapply(ad.df, is.numeric))],method="pearson")
M
corrplot(M,method="circle")


```
## Machine Learning Models

## Removing the variables ad topic, city,country,Timestamp  which is of not gretaer importance to model

```{r}

ad.df<-select (ad.df,-c(Ad.Topic.Line,City,Country,Timestamp))

```


## Split the dataset into train and test

```{r}

set.seed(1) # Set the seed for the  random number generator for reproducing the
# partition.
train.index <- sample(c(1:dim(ad.df)[1]), dim(ad.df)[1]*0.7)
test.index <- setdiff(c(1:dim(ad.df)[1]), train.index)
train.df <- ad.df[train.index, ]
test.df <- ad.df[test.index, ]


```



### Using Logistic regression buid the model

```{r}

lm.fit <- glm(Clicked.on.Ad ~., data = train.df, family = "binomial")
summary(lm.fit)

```

### Predicting the model using test dataset

```{r}
# evaluate
predictlm <- predict(lm.fit, test.df)

predictlm<-ifelse(predictlm > 0.5, 1, 0)

```


### Evaluate the model Accuracy

```{r}
library(caret)
cmt1<-confusionMatrix(as.factor(predictlm),as.factor(test.df$Clicked.on.Ad))
cmt1
```





### Naive bayes

```{r}
library(e1071)
ad.nb <- naiveBayes(Clicked.on.Ad ~ ., data = train.df)
ad.nb

```

## Predicting the model using test dataset
 
```{r}

predict_nb<- predict(ad.nb, newdata = test.df)
cm2<-confusionMatrix(as.factor(predict_nb), as.factor(test.df$Clicked.on.Ad))
cm2
```

## Decision tree

```{r}

ad_dt <-rpart(Clicked.on.Ad ~ ., data = train.df)
prp(ad_dt, type = 1, extra = 1, split.font = 1, varlen =-10)
```


### Predicting the model using test dataset


```{r}

predict_dt<-predict(ad_dt,test.df,type="prob")
predict_dt <- ifelse(predict_dt>0.5,1,0)
predict_dt <- factor(colnames(predict_dt)[max.col(predict_dt)])
cm3 <-confusionMatrix(as.factor(predict_dt),as.factor(test.df$Clicked.on.Ad))
cm3


```

## Model comparison based on accuracy

```{r}


accuracy <- data.frame(round(cmt1$overall*100,3),round(cm2$overall*100,3),
                 round(cm3$overall*100,3))


names(accuracy) <- c("Logistic","NaiveBayes","DecisionTree")

model_compare <- data.frame(Model = c('Logistic',
                                      'NaiveBayes',
                                      'DecisionTree'
                                      ),
                            Accuracy = c(accuracy$Logistic[1],
                                         accuracy$NaiveBayes[1],
                                         accuracy$DecisionTree[1]
                                         ))

ggplot(aes(x=Model, y=Accuracy,fill=Model), data=model_compare) +
    geom_bar(stat='identity')  +
       geom_text(aes(label = Accuracy), size = 3,position=position_dodge(0.9))+
    ggtitle('Comparative Accuracy of Models on Cross-Validation Data') +
    xlab('Models') +
    ylab('Overall Accuracy')

```
